## CXCL12/CXCR4 in the BLA

Finally, it should be noted that 



### Cellular distribution of CXCL12 and CXCR4 in the rat BLA

To explore how CXCL12 affects local communication between neurons and glia in the BLA, immunohistochemical double staining for CXCR4 in this area was performed with <!--nestin, DCX, NeuN, CD34, fetal liver kinase (Flk)-1, and CD31-->. 

Depletion of astroglia in both BLA and CeA was confirmed by immunofluorescent staining using GFAP antibody in a subset of f...-incubated slices.


### CXCL12 does not significantly modulate the electrophysiological actions in the BLA

``` {r CXCL12BLAstats, echo = FALSE, message= FALSE, echo = FALSE, warning = FALSE, message = FALSE, fig.width= 15, fig.height= 18}
CXCL12_BLA_membr_stat_all <- stat_table_exp_membr_extended((BLA_df_final_12))
BLA_sEPSC_final_12$Experiment <- as.factor(BLA_sEPSC_final_12$Experiment)
BLA_sEPSC_final_12$Cell <- as.factor(BLA_sEPSC_final_12$Cell)
BLA_sEPSC_final_12$Condition <- as.factor(BLA_sEPSC_final_12$Condition)
CXCL12_BLA_sEPSC_stat_all <- stat_table_exp_syn_extended(BLA_sEPSC_final_12)
CXCL12_2nM_BLA_sEPSC_stat_all <- CXCL12_BLA_sEPSC_stat_all %>% dplyr::filter(Experiment == 'CXCL12(2nM)')
CXCL12_2nM_BLA_sEPSC_stat_freq <- CXCL12_2nM_BLA_sEPSC_stat_all$Statistics[1]
CXCL12_5nM_BLA_sEPSC_stat_all <- CXCL12_BLA_sEPSC_stat_all %>% dplyr::filter(Experiment == 'CXCL12(5nM)')
CXCL12_5nM_BLA_sEPSC_stat_freq <- CXCL12_5nM_BLA_sEPSC_stat_all$Statistics[1]
```

To study whether BLA network can be regulated by CXCL12, whole-cell patch-clamp recordings were obtained from principal cells.<!--, measuring their excitability and intrinsic properties, as well as synaptic transmission.-->
The intrinsic membrane properties and synaptic transmission were measured using analogous protocols as in the CX3CL1 study. 
Regarding principal cells' excitability, at 2nM, CXCL12 does not affect this parameters (<!--ANOVA?--> \@ref(fig:CXCL12BLAintrinsic)a), whereas 5nM concentration of CXCL12 seems to enhance the excitability although the variation is high (\@ref(fig:(CXCL12BLAintrinsic)b).
This issue warrants further investigation.
Moreover, there was no observed difference in any PCs' measured membrane parameters (see: Appendix \@ref()). <!-- ładniej napisać-->

Similarly, to evaluate the potential contribution of the chemokine CXCL12 in the modulation of excitatory synaptic transmission, the frequency, amplitude, and kinetics of sEPSCs were analyzed.
Although, as shown in Fig.\@ref(fig:CXCL12BLAsEPSCfreq), it is tempting to speculate that while the concentration of 2nM does reduce the sEPSC... a partial reduction between NMDA and NMDA/CX3CL1 treated cells was observed, they were not statistical significant (`r CXCL12_2nM_BLA_sEPSC_stat_freq` and `r CXCL12_5nM_BLA_sEPSC_stat_freq`, respectively). 
These findings also need further replication and investigation of the potential underlying mechanisms.




```{r CXCL12BLAintrinsic, fig.cap='**2nM and 5nM CXCL12 does not affect BLA excitability** **(a1-a2)** Plots presenting population data of neurons before (blue) and after(red) CXCL12 treatment as a function of the frequency and injected depolarizing current steps', fig.align = 'center', echo = FALSE, message= FALSE, echo = FALSE, warning= FALSE, message = FALSE, fig.width= 8, fig.height= 5}
# IV grouped and individual
gr_BLA_c2 <- BLA_df_final_12 %>% filter(Experiment == "CXCL12(2nM)") %>% plot_IV_group_fixed(mtitle = "CXCL12(2nM)", Sweep_min = 0, Sweep_max = 500, Div = 20)
gr_BLA_c5 <- BLA_df_final_12 %>% filter(Experiment == "CXCL12(5nM)") %>% plot_IV_group_fixed(mtitle = "CXCL12(5nM)", Sweep_min = 0, Sweep_max = 500, Div = 20)

figure1 <- ((gr_BLA_c2 | gr_BLA_c5) + plot_layout(tag_level = 'new'))

figure1
```

```{r CXCL12BLAsEPSCfreq, fig.cap='**Effects of 2nM and 5nM CXCL12 on the frequency of sEPSCs** **(a1-a2)** Plots presenting population data of neurons before (blue) and after(red) CXCL12 treatment as a function of the frequency and injected depolarizing current steps', fig.align = 'center', echo = FALSE, message= FALSE, echo = FALSE, warning= FALSE, message = FALSE, fig.width= 8, fig.height= 5}

bp_BLA_freq <- plot_boxplot(BLA_sEPSC_final_12, median_Frequency, ylabel = "sEPSC Frequency (Hz)", vary1 = 0, vary2 = 12, dot_size = 2,  mtitle = "") 
bp_BLA_freq <- bp_BLA_freq + facet_wrap(~ Experiment, nrow = 1, scales = "free_x") + theme(plot.title = element_text(size= 16, face="bold"), axis.text.x = element_text(angle = 30, vjust = 0.7, hjust=0.5), strip.text = element_text(size = 11, face="bold"), strip.background = element_blank())

figure1 <- bp_BLA_freq /
           (+ plot_layout(tag_level = 'new'))

figure1
```


## CXCL12/CXCR4 in the CeA

These effects of SDF-1 were mediated *via* CXCR4 as they were abrogated by administration of a selective CXCR4 antagonist.

### Cellular distribution of CXCL12 and CXCR4 in the rat CeA

### CXCL12/CXCR4 modulation of the electrical properties in CeA neurons

AMD3100 eliminates the beneficial effects of CXCL12, indicating that the CXCL12/CXCR4 signaling pathway is vitally important in improving the neurobehavioral outcomes of ischemic mice, so studies were performed to detect the expression of CXCR4. 



##### inspiration

###### general

We first asked how...
To address this question, it was first determined the properties of ...

On the basis of our results, we conclude that

our finding of  …, …, …, support the hypothesis that 

More generally, our data significantly extend the understanding of glial functions  by showing that microglia are actively regulating inhibitory synapses

To investigate the effect of AZD8797 on chronic proinflammatory environment in the NTS, we analyzed the levels

###### electrophysiology

Around 75% of BLA neurons showed responsiveness to MCP-1/CCL2. 
The effect was not inhibited when GTP was omitted from the patch pipette medium (Fig. 8b, right).

The representative traces of sEPSCs in the absence (referred to as control hereafter) or presence of harmine (10μM) (referred to as harmine) were shown in supplemental Fig. S1(A)

To elucidate how IFNg affects nociceptive responses in the spinal dorsal horn, we analyzed the effects of IFNg on postsynaptic action by using whole-cell patch-clamp recordings from SG neurons.

To determine the nature of local connections between neurons in the CeL, paired whole-cell recordings were made in acute coronal slices of wild-type mice (Fig. - Hunt2017

To investigate the effect of <!--minocycline on inhibitory transmission-->, whole-cell voltage-clamp recordings from SG neurons were made under control conditions and after bath application of minocycline (100 lM)

Taken together, our findings indicate that minocycline increases the frequency of sIPSCs in a concentration-dependent manner (EC50 of 85 lM) without changing their amplitude, suggesting a presynaptic mechanism that contributes to the effect of minocycline

2.1-fold 2 r 4 in the spontaneous postsynaptic currents was elicited by GRO a 50 nM even in the presence of TTX 3 m M indicating that the action of the chemokine was exerted on neurotransmitter release mechanisms rather than on nerve cell excitability

To further examine whether neuronal activity contributes to the increase in sIPSC frequency produced by minocycline, we next tested whether TTX affected the response of minocycline. 

Therefore, we hypothesized that intrathecal administration of CCL2 would enhance spinal nociceptive transmission and cause thermal hyperalgesia by activating the spinal microglia. 
This hypothesis was tested using intrathecal administration of minocycline, a specific inhibitor of microglial activation [38,39]. 
Previous studies [40,41] showed that an intrathecal injection of minocycline (100 μg) blocked microglial activation.

AMPA-mediated spontaneous and mEPSC frequency is increased in EAE without change in the probability of release 
To determine whether the change in frequency between CFA and EAE was caused by alteration of unitary synaptic properties, we recorded mEPSCs after bath applying the sodium channel blocker, TTX. 

The amplitudes of mEPSCs reflect the number and conductance of subsynaptic AMPARs, whereas the frequency reflects the probability of vesicle release (p) and/or the number of synapses (Kerchner and Nicoll, 2008).

We found that mEPSC frequency was significantly increased (....) without any change in mEPSC amplitude.

The results suggest that IFNg enhances NMDA receptor signaling by activating IFNg receptors in the dorsal horn of the spinal cord. 
Minocycline, an inhibitor of microglial activation, inhibited the IFNg-induced facilitation of NMDA current, but inhibition of the neuronal JAK- STAT signaling did not. 
Therefore, we conclude that IFNg binds its own receptors in microglia but not SG neurons, and the subsequent microglial activation leads to NMDA receptor activation. - Sonekatsu2016

In a subset of experiments, slices were incubated in ACSF supplemented with  hyperpolarization-activated cation-nonselective (HCN) channels selective antagonists, ZD7288 (10 $\upmu$M) to verify whether the action of lamotrigine was HCN-dependent.

####### electro conclusion

These  studies indicate   the   direct   relationship   between   stress   and   GABA modulation in the amygdala.

####### silent synapses

An increased number of synapses could result from more dendritic spines and/or unsilencing of silent synapses.
In a silent synapse, an EPSC is absent because of a postsynaptic complement exclusively of NMDA receptors; hence, in the absence of depolarization, it cannot conduct current in response to presynaptic glutamate release. 
In response to sufficient depolarization, AMPARs can be inserted in the postsynaptic density, thereby making the synapse active or “unsilenced.” 
To this end, we measured the maximum amplitude of the eEPSC at -70 mV (AMPAR-mediated) and then at 40 mV, at a 50 ms latency (NMDA-mediated), both in the presence of picrotoxin (Fig. 2A).

significantly inhibited the amplitude of electrically evoked GABAergic IPSCs elicited from both the LPC and local synapses (Figure 3a). 

The inhibition of GABAergic transmission by 10mM PD128907 did not recover during an extensive washout period.
Despite this, the pipette resistance did not significantly change during the duration of these recordings.

Since microglia is an upstream partner of astrocytes in response to stimuli (Pascual et al., 2012), we next examined whether astrocyte activation will affect sIPSCs - Peng


The above observations suggest that minocycline may decrease neuronal excitability in a concentration- and cell-type-dependent manner by decreasing glutamatergic transmission.

Do these synaptic changes affect neuronal firing?

To understand the intracellular activity during SWs (SWi), simultaneous whole-cell recordings were obtained from BLA neurons. 

To gain insight into the inhibitory regulation of the local hippocampal circuitry, we examined the functional characteristic of the IPSCs in DG granule cells (Figure 1) and CA3 pyramidal neurons (Figure 2) in the dorsal and ventral hippocampus.

Comparison of neurochemical GABAergic synapse labeling between cell types showed that BLA interneurons receive a significantly higher density of putative GABAergic synapses compared with principal cells (Figs. 7 and 8).

This was also accompanied by significant increases in the frequency of sIPSCs (Fig. 9 and Table 3) compared with principal cells.



Of these cells, nine were classed as type 1 and the other nine as type 2

Quantitative analysis of GABAergic synapse markers and measurement of miniature inhibitory postsynaptic currents in BLA projection neurons after neurofascin knockdown ex vivo confirmed the loss of GABAergic input.

We were next interested in determining if lamotrigine affects GABAergic synaptic transmission in the hippocampus, a brain area critically involved in the coordination of neuronal activity that gives rise to network oscillations by GABAergic interneurons. 

###### immuno


###### dendrites

To analyze <!--the afferent connectivity of fully mature newborn granule neurons-->, we examined the dendritic spines of <!--8-weekold RFP+ cells -->.
These spines can be classified into various typologies on the basis of morphological criteria (Pallas-Bazarra et al., 2016; Pallas-Bazarra et al., 2017). <!--dać publikacje zespołu Jakuba-->

Fig. 4A and B shows representative images of dendritic fragments of <!--newborn neurons of WT (A) and CX3CR1?/? (B) animals -->. 
In addition, the classification of dendritic spines into mushroom, thin and stubby types is illustrated. 
Neurons <!--of CX3CR1?/? mice--> showed a reduction in the total number of dendritic spines.
To further characterize the populations of spines present in these cells, we measured the percentage of each type of spine (D).
As shown, the percentage of stubby spines was increased in CX3CR1?/? animals, whereas that of mushroom spines was reduced. 
Thus, these data show that the absence of CX3CR1 leads to a decrease in the number of newborn granule neuron dendritic spines and alterations in their morphology (namely, an enlargement and shortening).

To confirm whether dendritic spine density was increased,

In addition, we also examined spine morphology because changes in spine morphology are believed to represent one mechanism by which synaptic activity leaves its imprint on neurons. This was concurrent with an increase in spines with well-defined heads, which is correlated with spine maturation.


###### CeL clustering

We first performed whole-cell patch-clamp recordings on cells and then made post hoc morphological reconstructions of the recorded cells. 

Because the onset of spikes varied in response to different current injections, we determined the spike delay ( Fig. 1 D ) of the first AP upon a just suprathreshold current (i.e., rheobase) injection. 
Moreover, we determined the first AP properties, including the peak amplitude, voltage threshold, half-width, maximal rising rate, and maximal falling rate (see Materials and Methods). 
In addition to AP phenotypes, ES and LS cells differed in their subthreshold membrane responses ( Fig. 1 D ).
In striking contrast to ES cells, LS cells exhibited a slow ascending ramp in response to subthreshold current injection and displayed a greater ramp ratio ( Table 1 ).

To further test whether ES and LS cells arise from two separate classes of CeL neurons or if they represent a single population of cells spanning a continuum of excitability, we analyzed several other physiological features ( Table 1 ) from all non-LTB neurons. 
Overall, four features (spike delay, ramp ratio, RMP, and rheobase) showed non-Gaussian distributions ( Fig. 1 E ). 
To divide these two distinct cell classes unbiasedly, we performed hierarchical cluster analysis from 90 randomly recorded CeL neurons based on these four features ( Cossart et al., 2006 ; Graves et al., 2012 ; also see Materials and Methods). Strikingly, the cluster dendrogram yielded two distinct neuron populations, LS and ES cells ( Fig. 1 F ). The spike delay of LS and ES neurons was 1776 21 ms (blue, n 	 50) and 834 88 ms (red, n 	 40), respectively ( p 0.0001; Wilcoxon rank-sum test; Table 1 ). In addition, the LS population exhibited a more hyperpolarized RMP and a larger rheobase ( Table 1 ). Similar to the dendrogram, the scatter-plot of spike delay versus ramp ratio revealed two distinctly nonoverlapping clusters ( Fig. 1 G ). Classification of cells with the arbitrary cutoff value (spike delay of 1.5 s) fell into two categories, which corresponded to the same two populations determined by the unbiased hierarchical cluster analysis. As a result, we classified neurons with a spike delay of 
 1.5 s at rheobase as the LS cells and the remainders as the ES cells in the subsequent experiments of this study.
 
Based on literature, we included following criteria: (1) adaptation ratio [@hunt_2017], (2) rheobase and RMS [@hou_2016], 


###### LTP BLA

Upon application of HFS, vSub-evoked field potentials in the BLA were effectively potentiated in the control group, but not in the NF knockdown group as revealed by mixed model repeated-measure ANOVA (group effect: (F (1,16) = 16.27, P = 0.001; and group × post-HFS time point interaction: F(2.071,33.136) = 9.231, P = 0.001, Greenhouse – Geisser correction; Figure 4f). The comparison of average potentiation across time points after induction also revealed a highly significant difference between the two groups (Figure 4g, t (16) = 4.03, P = 0.001).

NF knockdown with the less effective NF1196 vector also reduced vSub-BLA LTP (Supplementary Figure S8b and c) without altering the input – output curve (Supplementary Figure S8a). Together, this demonstrates a specific impairment of BLA synaptic plasticity to vSub inputs after NF knockdown. 

<!-- 
The effect of **500 pM CX3CL1** on LTP in the DG was investigated both in the presence and absence of 100 μM of the GABAA receptor/chloride channel inhibitor, picrotoxin (Sigma–Aldrich).-Sheridan2014
-->

<!-- We decided to use, in all future experiments, 100 nM of CXCL16 since, at this concentration, neuronal cell death was efficiently prevented 
At all the tested concentrations, CXCL16 per se was not toxic (data not shown). 
Hyaluronidase does not significantly affect neuronal 0electrophysiological properties when applied solely,

 We chose a dose that does not activate basal HPA axis activity
 
 The dorsal and ventral parts of the local hippocampal neuronal networks participate in different extended circuitries (Papatheodoropoulos, 2018; Strange et al., 2014) and hence, the inhibitory input of the intrinsic primary hippocampal circuitry may vary and differentially regulate the local network. To gain insight into the inhibitory regulation of the local hippocampal circuitry, we examined the functional characteristic of the IPSCs in DG granule cells (Figure 1) and CA3 pyramidal neurons (Figure 2) in the dorsal and ventral hippocampus.
-->
<!--  As reported in Figure 2,  .... in response to exogenously administrated CXCL16  in a concentration-dependent way, with an effect that is maximal at  0.1 nM-->



In order to maintain stable functionality in the face of continually changing input, neurones in  the CNS must dynamically modulate their electrical characteristics. It