# Appendix {#appendix}

## Suplementary data {#suppdata}

### CX3CL1 does not affect passive membrane properties of principal cells in the BLA {#CX3CL1_membrane_appendix}

In Figure (\@ref(fig:CX3CL1_BLA_excitability_fig_all)) and Table (\@ref(tab:CX3CL1_BLA_excitability_appendix)) below are depicted and listed all the passive membrane properties measured in the principal cells in the BLA following CX3CL1 treatment. 

```{r CX3CL1_BLA_excitability_appendix, echo= FALSE, message= FALSE, warning = FALSE, error = FALSE, results='asis'}
# getting the table of statistics
CX3CL1_BLA_stat_df <- formattable(stat_table_exp_membr_extended((BLA_df_final)))

# kable not working with those complex table
# knitr::kable(CX3CL1_BLA_stat_df, booktabs = TRUE,
#  caption = 'The table of all of measured passive membrane parameters in the BLA following CX3CL1 application with all the conditions'
# ) 

library(gt)

table <- CX3CL1_BLA_stat_df %>% 
gt(groupname_col = "Variable") %>%
   fmt_markdown(columns = c("Experiment")) %>%
    tab_options(
      table.font.names = "Calibri",
      table.font.size = 12
  ) %>% #table.font.size = 11
#  tab_options(
 #   table.width = pct(100)) %>%
      tab_style(
    style = list(
      cell_text(weight = "bold")
      ),
    locations = cells_row_groups()
  ) %>%
    opt_row_striping() %>%
      tab_header(
    title = ("Table 7.1. Statistics of all measured parameters in relation to BLA principal cells membrane properties following CX3CL1 application"),
     subtitle = md("")) %>%
    opt_row_striping() %>%
   tab_source_note(source_note = md(""))  %>%
             gtsave("CX3CL1_membrane_table.html")
```

```{r CX3CL1_BLA_excitability_fig_all, fig.cap= '', fig.align = 'center', echo= FALSE, message= FALSE, warning = FALSE, error = FALSE, results='asis', fig.height= 40, fig.width= 20}
# GAIN
bp_BLA_gain <- plot_boxplot(BLA_df_final, gain, mtitle= "BLA - principal cells", ylabel = "gain",  dot_size = 2)
bp_BLA_gain <- bp_BLA_gain + facet_wrap(~ Experiment, nrow = 1, scales = "free_x") + theme(plot.title = element_text(size= 16, face="bold"), axis.text.x = element_text(angle = 30, vjust = 0.7, hjust=0.5)) + stat_compare_means(method = 't.test', hide.ns = TRUE, label = 'p.signif', paired = TRUE, label.x.npc = 'center', var.equal = TRUE)

bp_BLA_inter_gain <- plot_boxplot(BLA_df_inter, gain, ylabel = "gain", mtitle = "BLA - interneurons", dot_size = 2)
bp_BLA_inter_gain <- bp_BLA_inter_gain + facet_wrap(~ Experiment, nrow = 1, scales = "free_x") + theme(plot.title = element_text(size= 16, face="bold"), axis.text.x = element_text(angle = 30, vjust = 0.7, hjust=0.5)) #+ stat_compare_means(method = 't.test', hide.ns = TRUE, label = 'p.signif', paired = TRUE, label.x.npc = 'center') + geom_text(x = 1.5, y = -20, aes(label = label, color = NULL, group= NULL), data = f_labels) #annotate("text", x = 1.5, y = -20, facet = 6, label = "*")


pie_BLA_frak_gain <- BLA_df_final %>% filter(Experiment == 'CX3CL1(2nM)') %>% plot_pie_val15(gain, "CX3CL1(2nM)") + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_frak5nM_gain <- BLA_df_final %>% filter(Experiment == 'CX3CL1(5nM)') %>% plot_pie_val15(gain, "CX3CL1(5nM)") + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_antifrak_gain <- BLA_df_final %>% filter(Experiment == 'anti-CX3CR1 + \nCX3CL1(2nM)') %>% plot_pie_val15(gain, 'anti-CX3CR1 + \nCX3CL1(2nM)') + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_azdfrak_gain <- BLA_df_final %>% filter(Experiment == 'AZD8797 + \nCX3CL1(2nM)') %>% plot_pie_val15(gain, "AZD8797 + \nCX3CL1(2nM)") + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_azd_gain <- BLA_df_final %>% filter(Experiment == "AZD8797") %>% plot_pie_val15(gain, "AZD8797") + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_minofrak_gain <- BLA_df_final %>% filter(Experiment == 'minocycline + \nCX3CL1(2nM)') %>% plot_pie_val15(gain, 'minocycline + \nCX3CL1(2nM)') + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_mino_gain <- BLA_df_final %>% filter(Experiment == 'minocycline') %>% plot_pie_val15(gain, "minocycline") + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_picro_gain <- BLA_df_final %>% filter(Experiment == 'picrotoxin + \nCGP52432 + \nCX3CL1(2nM)') %>% plot_pie_val15(gain, 'picrotoxin + \nCGP52432 + \nCX3CL1(2nM)') + theme(plot.title = element_text(size= 10, hjust = 0.5))


# THRESHOLD CURRENT
f_labels_BLA_thres <- data.frame(Experiment = c( c("CX3CL1(2nM)" , "CX3CL1(5nM)", 'anti-CX3CR1 + \nCX3CL1(2nM)', "AZD8797 + \nCX3CL1(2nM)", "AZD8797", 'minocycline + \nCX3CL1(2nM)' , "minocycline" , 'picrotoxin + \nCGP52432 + \nCX3CL1(2nM)' )), label = c("", "", "", "", "", "", "*", ""))
f_labels_BLA_thres$Experiment <- factor(f_labels_BLA_thres$Experiment, levels = c("CX3CL1(2nM)" , "CX3CL1(5nM)", 'anti-CX3CR1 + \nCX3CL1(2nM)', "AZD8797 + \nCX3CL1(2nM)", "AZD8797", 'minocycline + \nCX3CL1(2nM)' , "minocycline" , 'picrotoxin + \nCGP52432 + \nCX3CL1(2nM)'))
bp_BLA_thres <- plot_boxplot(BLA_df_final, Treshold1_all, ylabel = "Threshold current (mV)", mtitle = "BLA", vary1 = -55, vary2 = -20, dot_size = 2)
bp_BLA_thres <- bp_BLA_thres + facet_wrap(~ Experiment, nrow = 1, scales = "free_x") + theme(plot.title = element_text(size= 16, face="bold"), axis.text.x = element_text(angle = 30, vjust = 0.7, hjust=0.5)) + stat_compare_means(method = 't.test', hide.ns = TRUE, label = 'p.signif', paired = TRUE, label.x.npc = 'center') + geom_text(x = 1.5, y = -20, aes(label = label, color = NULL, group= NULL), data = f_labels_BLA_thres) #annotate("text", x = 1.5, y = -20, facet = 6, label = "*")

bp_BLA_inter_thres <- plot_boxplot(BLA_df_inter, Treshold1_all, ylabel = "Threshold current (mV)", mtitle = "BLA - interneurons", vary1 = -50, vary2 = -30, dot_size = 2)
bp_BLA_inter_thres <- bp_BLA_inter_thres + facet_wrap(~ Experiment, nrow = 1, scales = "free_x") + theme(plot.title = element_text(size= 16, face="bold"), axis.text.x = element_text(angle = 30, vjust = 0.7, hjust=0.5)) #+ stat_compare_means(method = 't.test', hide.ns = TRUE, label = 'p.signif', paired = TRUE, label.x.npc = 'center') + geom_text(x = 1.5, y = -20, aes(label = label, color = NULL, group= NULL), data = f_labels) #annotate("text", x = 1.5, y = -20, facet = 6, label = "*")

pie_BLA_frak_thres <- BLA_df_final %>% filter(Experiment == 'CX3CL1(2nM)') %>% plot_pie_val3(Treshold1_all, "CX3CL1(2nM)") + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_frak5nM_thres <- BLA_df_final %>% filter(Experiment == 'CX3CL1(5nM)') %>% plot_pie_val3(Treshold1_all, "CX3CL1(5nM)") + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_antifrak_thres <- BLA_df_final %>% filter(Experiment == 'anti-CX3CR1 + \nCX3CL1(2nM)') %>% plot_pie_val3(Treshold1_all, 'anti-CX3CR1 + \nCX3CL1(2nM)') + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_azdfrak_thres <- BLA_df_final %>% filter(Experiment == 'AZD8797 + \nCX3CL1(2nM)') %>% plot_pie_val3(Treshold1_all, "AZD8797 + \nCX3CL1(2nM)") + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_azd_thres <- BLA_df_final %>% filter(Experiment == "AZD8797") %>% plot_pie_val3(Treshold1_all, "AZD8797") + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_minofrak_thres <- BLA_df_final %>% filter(Experiment == 'minocycline + \nCX3CL1(2nM)') %>% plot_pie_val3(Treshold1_all, 'minocycline + \nCX3CL1(2nM)') + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_mino_thres <- BLA_df_final %>% filter(Experiment == 'minocycline') %>% plot_pie_val3(Treshold1_all, "minocycline") + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_picro_thres <- BLA_df_final %>% filter(Experiment == 'picrotoxin + \nCGP52432 + \nCX3CL1(2nM)') %>% plot_pie_val3(Treshold1_all, 'picrotoxin + \nCGP52432 + \nCX3CL1(2nM)') + theme(plot.title = element_text(size= 10, hjust = 0.5))


# ADAPTATION
bp_BLA_adap <- plot_boxplot(BLA_df_final, Adaptation_ratio, ylabel = "Adaptation ratio", mtitle = "BLA", vary1 = 0, vary2 = 1.5, dot_size = 2)
bp_BLA_adap <- bp_BLA_adap + facet_wrap(~ Experiment, nrow = 1, scales = "free_x") + theme(plot.title = element_text(size= 16, face="bold"), axis.text.x = element_text(angle = 30, vjust = 0.7, hjust=0.5)) + stat_compare_means(method = 't.test', hide.ns = TRUE, label = 'p.signif', paired = TRUE, label.x.npc = 'center', var.equal = TRUE)

bp_BLA_inter_adap <- plot_boxplot(BLA_df_inter, Adaptation_ratio, ylabel = "Adaptation ratio", mtitle = "BLA - interneurons", vary1 = 0, vary2 = 1.5, dot_size = 2)
bp_BLA_inter_adap <- bp_BLA_inter_adap + facet_wrap(~ Experiment, nrow = 1, scales = "free_x") + theme(plot.title = element_text(size= 16, face="bold"), axis.text.x = element_text(angle = 30, vjust = 0.7, hjust=0.5)) #+ stat_compare_means(method = 't.test', hide.ns = TRUE, label = 'p.signif', paired = TRUE, label.x.npc = 'center', var.equal = TRUE)


pie_BLA_frak_adap <- BLA_df_final %>% filter(Experiment == 'CX3CL1(2nM)') %>% plot_pie2(Adaptation_ratio, "CX3CL1(2nM)") + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_frak5nM_adap <- BLA_df_final %>% filter(Experiment == 'CX3CL1(5nM)') %>% plot_pie2(Adaptation_ratio, "CX3CL1(5nM)") + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_antifrak_adap <- BLA_df_final %>% filter(Experiment == 'anti-CX3CR1 + \nCX3CL1(2nM)') %>% plot_pie2(Adaptation_ratio, 'anti-CX3CR1 + \nCX3CL1(2nM)') + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_azdfrak_adap <- BLA_df_final %>% filter(Experiment == 'AZD8797 + \nCX3CL1(2nM)') %>% plot_pie2(Adaptation_ratio, "AZD8797 + \nCX3CL1(2nM)") + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_azd_adap <- BLA_df_final %>% filter(Experiment == "AZD8797") %>% plot_pie2(Adaptation_ratio, "AZD8797") + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_minofrak_adap <- BLA_df_final %>% filter(Experiment == 'minocycline + \nCX3CL1(2nM)') %>% plot_pie2(Adaptation_ratio, 'minocycline + \nCX3CL1(2nM)') + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_mino_adap <- BLA_df_final %>% filter(Experiment == 'minocycline') %>% plot_pie2(Adaptation_ratio, "minocycline") + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_picro_adap <- BLA_df_final %>% filter(Experiment == 'picrotoxin + \nCGP52432 + \nCX3CL1(2nM)') %>% plot_pie2(Adaptation_ratio, 'picrotoxin + \nCGP52432 + \nCX3CL1(2nM)') + theme(plot.title = element_text(size= 10, hjust = 0.5))


# INPUT RESISTANCE
f_labels_BLA_rm <- data.frame(Experiment = c( c("CX3CL1(2nM)" , "CX3CL1(5nM)", 'anti-CX3CR1 + \nCX3CL1(2nM)' ,"AZD8797 + \nCX3CL1(2nM)", "AZD8797", 'minocycline + \nCX3CL1(2nM)' , "minocycline" , 'picrotoxin + \nCGP52432 + \nCX3CL1(2nM)' )), label = c("", "", "", "", "", "", "*", ""))
f_labels_BLA_rm$Experiment <- factor(f_labels_BLA_rm$Experiment, levels = c("CX3CL1(2nM)" , "CX3CL1(5nM)", 'anti-CX3CR1 + \nCX3CL1(2nM)' ,"AZD8797 + \nCX3CL1(2nM)", "AZD8797", 'minocycline + \nCX3CL1(2nM)' , "minocycline" , 'picrotoxin + \nCGP52432 + \nCX3CL1(2nM)'))
bp_BLA_rm <- plot_boxplot(BLA_df_final, Rm_20, ylabel = "Input resistance (MOhm)", mtitle = "BLA", vary1 = 0, vary2 = 250, dot_size = 2)
bp_BLA_rm <- bp_BLA_rm + facet_wrap(~ Experiment, nrow = 1, scales = "free_x") + theme(plot.title = element_text(size= 16, face="bold"), axis.text.x = element_text(angle = 30, vjust = 0.7, hjust=0.5)) + stat_compare_means(method = 't.test', hide.ns = TRUE, label = 'p.signif', paired = TRUE, label.x.npc = 'center') + geom_text(x = 1.5, y = 800, aes(label = label, color = NULL, group= NULL), data = f_labels_BLA_rm)

bp_BLA_inter_rm <- plot_boxplot(BLA_df_inter, Rm_20, ylabel = "Input resistance (MOhm)", mtitle = "BLA - interneurons", vary1 = 80, vary2 = 320, dot_size = 2)
bp_BLA_inter_rm <- bp_BLA_inter_rm + facet_wrap(~ Experiment, nrow = 1, scales = "free_x") + theme(plot.title = element_text(size= 16, face="bold"), axis.text.x = element_text(angle = 30, vjust = 0.7, hjust=0.5)) #+ stat_compare_means(method = 't.test', hide.ns = TRUE, label = 'p.signif', paired = TRUE, label.x.npc = 'center') + geom_text(x = 1.5, y = 800, aes(label = label, color = NULL, group= NULL), data = f_labels)

pie_BLA_frak_rm <- BLA_df_final %>% filter(Experiment == 'CX3CL1(2nM)') %>% plot_pie2(Rm_20, "CX3CL1(2nM)") + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_frak5nM_rm <- BLA_df_final %>% filter(Experiment == 'CX3CL1(5nM)') %>% plot_pie2(Rm_20, "CX3CL1(5nM)") + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_antifrak_rm <- BLA_df_final %>% filter(Experiment == 'anti-CX3CR1 + \nCX3CL1(2nM)') %>% plot_pie2(Rm_20, 'anti-CX3CR1 + \nCX3CL1(2nM)') + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_azdfrak_rm <- BLA_df_final %>% filter(Experiment == 'AZD8797 + \nCX3CL1(2nM)') %>% plot_pie2(Rm_20, "AZD8797 + \nCX3CL1(2nM)") + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_azd_rm <- BLA_df_final %>% filter(Experiment == "AZD8797") %>% plot_pie2(Rm_20, "AZD8797") + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_minofrak_rm <- BLA_df_final %>% filter(Experiment == 'minocycline + \nCX3CL1(2nM)') %>% plot_pie2(Rm_20, 'minocycline + \nCX3CL1(2nM)') + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_mino_rm <- BLA_df_final %>% filter(Experiment == 'minocycline') %>% plot_pie2(Rm_20, "minocycline") + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_picro_rm <- BLA_df_final %>% filter(Experiment == 'picrotoxin + \nCGP52432 + \nCX3CL1(2nM)') %>% plot_pie2(Rm_20, 'picrotoxin + \nCGP52432 + \nCX3CL1(2nM)') + theme(plot.title = element_text(size= 10, hjust = 0.5))


# TAU
bp_BLA_tau <- plot_boxplot(BLA_df_final, tau_20, ylabel = "tau (ms)", mtitle = "BLA", vary1 = 0, vary2 = 40, dot_size = 2)
bp_BLA_tau <- bp_BLA_tau + facet_wrap(~ Experiment, nrow = 1, scales = "free_x") + theme(plot.title = element_text(size= 16, face="bold"), axis.text.x = element_text(angle = 30, vjust = 0.7, hjust=0.5)) + stat_compare_means(method = 't.test', hide.ns = TRUE, label = 'p.signif', paired = TRUE, label.x.npc = 'center', var.equal = TRUE)

bp_BLA_inter_tau <- plot_boxplot(BLA_df_inter, tau_20, ylabel = "tau (ms)", mtitle = "BLA - interneurons", vary1 = 0, vary2 = 25, dot_size = 2)
bp_BLA_inter_tau <- bp_BLA_inter_tau + facet_wrap(~ Experiment, nrow = 1, scales = "free_x") + theme(plot.title = element_text(size= 16, face="bold"), axis.text.x = element_text(angle = 30, vjust = 0.7, hjust=0.5)) #+ stat_compare_means(method = 't.test', hide.ns = TRUE, label = 'p.signif', paired = TRUE, label.x.npc = 'center', var.equal = TRUE)


pie_BLA_frak_tau <- BLA_df_final %>% filter(Experiment == 'CX3CL1(2nM)') %>% plot_pie2(tau_20, "CX3CL1(2nM)") + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_frak5nM_tau <- BLA_df_final %>% filter(Experiment == 'CX3CL1(5nM)') %>% plot_pie2(tau_20, "CX3CL1(5nM)") + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_antifrak_tau <- BLA_df_final %>% filter(Experiment == 'anti-CX3CR1 + \nCX3CL1(2nM)') %>% plot_pie2(tau_20, 'anti-CX3CR1 + \nCX3CL1(2nM)') + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_azdfrak_tau <- BLA_df_final %>% filter(Experiment == 'AZD8797 + \nCX3CL1(2nM)') %>% plot_pie2(tau_20, "AZD8797 + \nCX3CL1(2nM)") + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_azd_tau <- BLA_df_final %>% filter(Experiment == "AZD8797") %>% plot_pie2(tau_20, "AZD8797") + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_minofrak_tau <- BLA_df_final %>% filter(Experiment == 'minocycline + \nCX3CL1(2nM)') %>% plot_pie2(tau_20, 'minocycline + \nCX3CL1(2nM)') + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_mino_tau <- BLA_df_final %>% filter(Experiment == 'minocycline') %>% plot_pie2(tau_20, "minocycline") + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_picro_tau <- BLA_df_final %>% filter(Experiment == 'picrotoxin + \nCGP52432 + \nCX3CL1(2nM)') %>% plot_pie2(tau_20, 'picrotoxin + \nCGP52432 + \nCX3CL1(2nM)') + theme(plot.title = element_text(size= 10, hjust = 0.5))

# CAPACITANCE
bp_BLA_cap <- plot_boxplot(BLA_df_final, C_20, ylabel = "Capacitance (pF)", mtitle = "BLA", vary1 = 90, vary2 = 500, dot_size = 2)
bp_BLA_cap <- bp_BLA_cap + facet_wrap(~ Experiment, nrow = 1, scales = "free_x") + theme(plot.title = element_text(size= 16, face="bold"), axis.text.x = element_text(angle = 30, vjust = 0.7, hjust=0.5)) + stat_compare_means(method = 't.test', hide.ns = TRUE, label = 'p.signif', paired = TRUE, label.x.npc = 'center', var.equal = TRUE)

bp_BLA_inter_cap <- plot_boxplot(BLA_df_inter, C_20, ylabel = "Capacitance (pF)", mtitle = "BLA - interneurons", vary1 = 30, vary2 = 300, dot_size = 2)
bp_BLA_inter_cap <- bp_BLA_inter_cap + facet_wrap(~ Experiment, nrow = 1, scales = "free_x") + theme(plot.title = element_text(size= 16, face="bold"), axis.text.x = element_text(angle = 30, vjust = 0.7, hjust=0.5)) # + stat_compare_means(method = 't.test', hide.ns = TRUE, label = 'p.signif', paired = TRUE, label.x.npc = 'center', var.equal = TRUE)


pie_BLA_frak_cap <- BLA_df_final %>% filter(Experiment == 'CX3CL1(2nM)') %>% plot_pie2(C_20, "CX3CL1(2nM)") + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_frak5nM_cap <- BLA_df_final %>% filter(Experiment == 'CX3CL1(5nM)') %>% plot_pie2(C_20, "CX3CL1(5nM)") + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_antifrak_cap <- BLA_df_final %>% filter(Experiment == 'anti-CX3CR1 + \nCX3CL1(2nM)') %>% plot_pie2(C_20, 'anti-CX3CR1 + \nCX3CL1(2nM)') + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_azdfrak_cap <- BLA_df_final %>% filter(Experiment == 'AZD8797 + \nCX3CL1(2nM)') %>% plot_pie2(C_20, "AZD8797 + \nCX3CL1(2nM)") + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_azd_cap <- BLA_df_final %>% filter(Experiment == "AZD8797") %>% plot_pie2(C_20, "AZD8797") + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_minofrak_cap <- BLA_df_final %>% filter(Experiment == 'minocycline + \nCX3CL1(2nM)') %>% plot_pie2(C_20, 'minocycline + \nCX3CL1(2nM)') + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_mino_cap <- BLA_df_final %>% filter(Experiment == 'minocycline') %>% plot_pie2(C_20, "minocycline") + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_picro_cap <- BLA_df_final %>% filter(Experiment == 'picrotoxin + \nCGP52432 + \nCX3CL1(2nM)') %>% plot_pie2(C_20, 'picrotoxin + \nCGP52432 + \nCX3CL1(2nM)') + theme(plot.title = element_text(size= 10, hjust = 0.5))


# SAG
bp_BLA_sag <- plot_boxplot(BLA_df_sag, sag_ratio_140, ylabel = "sag ratio @-140 pA", mtitle = "BLA", dot_size = 2)
bp_BLA_sag <- bp_BLA_sag + facet_wrap(~ Experiment, nrow = 1, scales = "free_x") + theme(plot.title = element_text(size= 16, face="bold"), axis.text.x = element_text(angle = 30, vjust = 0.7, hjust=0.5)) + stat_compare_means(method = 't.test', hide.ns = TRUE, label = 'p.signif', paired = TRUE, label.x.npc = 'center', var.equal = TRUE)

bp_BLA_inter_sag <- plot_boxplot(BLA_df_inter_sag, sag_ratio_140, ylabel = "sag ratio @-140 pA", mtitle = "BLA - interneurons", dot_size = 2)
bp_BLA_inter_sag <- bp_BLA_inter_sag + facet_wrap(~ Experiment, nrow = 1, scales = "free_x") + theme(plot.title = element_text(size= 16, face="bold"), axis.text.x = element_text(angle = 30, vjust = 0.7, hjust=0.5)) #+ stat_compare_means(method = 't.test', hide.ns = TRUE, label = 'p.signif', paired = TRUE, label.x.npc = 'center', var.equal = TRUE)

pie_BLA_frak_sag <- BLA_df_sag %>% filter(Experiment == 'CX3CL1(2nM)') %>% plot_pie_val3(sag_ratio_140, "CX3CL1(2nM)") + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_frak5nM_sag <- BLA_df_sag %>% filter(Experiment == 'CX3CL1(5nM)') %>% plot_pie_val3(sag_ratio_140, "CX3CL1(5nM)") + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_antifrak_sag <- BLA_df_sag %>% filter(Experiment == 'anti-CX3CR1 + \nCX3CL1(2nM)') %>% plot_pie_val3(sag_ratio_140, 'anti-CX3CR1 + \nCX3CL1(2nM)') + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_azdfrak_sag <- BLA_df_sag %>% filter(Experiment == 'AZD8797 + \nCX3CL1(2nM)') %>% plot_pie_val3(sag_ratio_140, "AZD8797 + \nCX3CL1(2nM)") + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_azd_sag <- BLA_df_sag %>% filter(Experiment == "AZD8797") %>% plot_pie_val3(sag_ratio_140, "AZD8797") + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_minofrak_sag <- BLA_df_sag %>% filter(Experiment == 'minocycline + \nCX3CL1(2nM)') %>% plot_pie_val3(sag_ratio_140, 'minocycline + \nCX3CL1(2nM)') + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_mino_sag <- BLA_df_sag %>% filter(Experiment == 'minocycline') %>% plot_pie_val3(sag_ratio_140, "minocycline") + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_picro_sag <- BLA_df_sag %>% filter(Experiment == 'picrotoxin + \nCGP52432 + \nCX3CL1(2nM)') %>% plot_pie_val3(sag_ratio_140, 'picrotoxin + \nCGP52432 + \nCX3CL1(2nM)') + theme(plot.title = element_text(size= 10, hjust = 0.5))



# RESTING MEMBRANE POTENTIAL
bp_BLA_vm <- plot_boxplot(BLA_df_final, RMS, ylabel = "Resting membrane potential (mV)", mtitle = "BLA", vary1 = -90, vary2 = -45, dot_size = 2)
bp_BLA_vm <- bp_BLA_vm + facet_wrap(~ Experiment, nrow = 1, scales = "free_x") + theme(plot.title = element_text(size= 16, face="bold"), axis.text.x = element_text(angle = 30, vjust = 0.7, hjust=0.5)) #+ stat_compare_means(method = 't.test', hide.ns = TRUE, label = 'p.signif', paired = TRUE, label.x.npc = 'center', var.equal = TRUE)

bp_BLA_inter_vm <- plot_boxplot(BLA_df_inter, RMS, ylabel = "Resting membrane potential (mV)", mtitle = "BLA - interneurons", vary1 = -80, vary2 = -40, dot_size = 2)
bp_BLA_inter_vm <- bp_BLA_inter_vm + facet_wrap(~ Experiment, nrow = 1, scales = "free_x") + theme(plot.title = element_text(size= 16, face="bold"), axis.text.x = element_text(angle = 30, vjust = 0.7, hjust=0.5)) #+ stat_compare_means(method = 't.test', hide.ns = TRUE, label = 'p.signif', paired = TRUE, label.x.npc = 'center', var.equal = TRUE)

pie_BLA_frak_vm <- BLA_df_final %>% filter(Experiment == 'CX3CL1(2nM)') %>% plot_pie_val3(RMS, "CX3CL1(2nM)") + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_frak5nM_vm <- BLA_df_final %>% filter(Experiment == 'CX3CL1(5nM)') %>% plot_pie_val3(RMS, "CX3CL1(5nM)") + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_antifrak_vm <- BLA_df_final %>% filter(Experiment == 'anti-CX3CR1 + \nCX3CL1(2nM)') %>% plot_pie_val3(RMS, 'anti-CX3CR1 + \nCX3CL1(2nM)') + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_azdfrak_vm <- BLA_df_final %>% filter(Experiment == 'AZD8797 + \nCX3CL1(2nM)') %>% plot_pie_val3(RMS, "AZD8797 + \nCX3CL1(2nM)") + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_azd_vm <- BLA_df_final %>% filter(Experiment == "AZD8797") %>% plot_pie_val3(RMS, "AZD8797") + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_minofrak_vm <- BLA_df_final %>% filter(Experiment == 'minocycline + \nCX3CL1(2nM)') %>% plot_pie_val3(RMS, 'minocycline + \nCX3CL1(2nM)') + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_mino_vm <- BLA_df_final %>% filter(Experiment == 'minocycline') %>% plot_pie_val3(RMS, "minocycline") + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_picro_vm <- BLA_df_final %>% filter(Experiment == 'picrotoxin + \nCGP52432 + \nCX3CL1(2nM)') %>% plot_pie_val3(RMS, 'picrotoxin + \nCGP52432 + \nCX3CL1(2nM)') + theme(plot.title = element_text(size= 10, hjust = 0.5))


# ACTION POTENTIAL WIDTH
bp_BLA_apw <- plot_boxplot(BLA_df_final, AP_width1_all, ylabel = "Action potential width (ms)", mtitle = "BLA", vary1 = 0.5, vary2 = 1.5, dot_size = 2)
bp_BLA_apw  <- bp_BLA_apw  + facet_wrap(~ Experiment, nrow = 1, scales = "free_x") + theme(plot.title = element_text(size= 16, face="bold"), axis.text.x = element_text(angle = 30, vjust = 0.7, hjust=0.5)) #+ stat_compare_means(method = 't.test', hide.ns = TRUE, label = 'p.signif', paired = TRUE, label.x.npc = 'center', var.equal = TRUE)

bp_BLA_inter_apw  <- plot_boxplot(BLA_df_inter, AP_width1_all, ylabel = "Action potential width (ms)", mtitle = "BLA - interneurons", vary1 = 0.5, vary2 = 1.5, dot_size = 2)
bp_BLA_inter_apw  <- bp_BLA_inter_apw  + facet_wrap(~ Experiment, nrow = 1, scales = "free_x") + theme(plot.title = element_text(size= 16, face="bold"), axis.text.x = element_text(angle = 30, vjust = 0.7, hjust=0.5)) #+ stat_compare_means(method = 't.test', hide.ns = TRUE, label = 'p.signif', paired = TRUE, label.x.npc = 'center', var.equal = TRUE)

pie_BLA_frak_apw  <- BLA_df_final %>% filter(Experiment == 'CX3CL1(2nM)') %>% plot_pie_val3(AP_width1_all, "CX3CL1(2nM)") + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_frak5nM_apw  <- BLA_df_final %>% filter(Experiment == 'CX3CL1(5nM)') %>% plot_pie_val3(AP_width1_all, "CX3CL1(5nM)") + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_antifrak_apw  <- BLA_df_final %>% filter(Experiment == 'anti-CX3CR1 + \nCX3CL1(2nM)') %>% plot_pie_val3(AP_width1_all, 'anti-CX3CR1 + \nCX3CL1(2nM)') + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_azdfrak_apw  <- BLA_df_final %>% filter(Experiment == 'AZD8797 + \nCX3CL1(2nM)') %>% plot_pie_val3(AP_width1_all, "AZD8797 + \nCX3CL1(2nM)") + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_azd_apw  <- BLA_df_final %>% filter(Experiment == "AZD8797") %>% plot_pie_val3(AP_width1_all, "AZD8797") + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_minofrak_apw  <- BLA_df_final %>% filter(Experiment == 'minocycline + \nCX3CL1(2nM)') %>% plot_pie_val3(AP_width1_all, 'minocycline + \nCX3CL1(2nM)') + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_mino_apw  <- BLA_df_final %>% filter(Experiment == 'minocycline') %>% plot_pie_val3(AP_width1_all, "minocycline") + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_picro_apw  <- BLA_df_final %>% filter(Experiment == 'picrotoxin + \nCGP52432 + \nCX3CL1(2nM)') %>% plot_pie_val3(AP_width1_all, 'picrotoxin + \nCGP52432 + \nCX3CL1(2nM)') + theme(plot.title = element_text(size= 10, hjust = 0.5))


# ACTION POTENTIAL AMPLITUDE
bp_BLA_apa <- plot_boxplot(BLA_df_final, AP_amp1_all, ylabel = "Action potential amplitude (pA)", mtitle = "BLA", vary1 = 50, vary2 = 120, dot_size = 2)
bp_BLA_apa <- bp_BLA_apa + facet_wrap(~ Experiment, nrow = 1, scales = "free_x") + theme(plot.title = element_text(size= 16, face="bold"), axis.text.x = element_text(angle = 30, vjust = 0.7, hjust=0.5)) #+ stat_compare_means(method = 't.test', hide.ns = TRUE, label = 'p.signif', paired = TRUE, label.x.npc = 'center', var.equal = TRUE)

bp_BLA_inter_apa <- plot_boxplot(BLA_df_inter, AP_amp1_all, ylabel = "Action potential amplitude (pA)", mtitle = "BLA - interneurons", vary1 = 40, vary2 = 90, dot_size = 2)
bp_BLA_inter_apa <- bp_BLA_inter_apa + facet_wrap(~ Experiment, nrow = 1, scales = "free_x") + theme(plot.title = element_text(size= 16, face="bold"), axis.text.x = element_text(angle = 30, vjust = 0.7, hjust=0.5)) #+ stat_compare_means(method = 't.test', hide.ns = TRUE, label = 'p.signif', paired = TRUE, label.x.npc = 'center', var.equal = TRUE)

pie_BLA_frak_apa <- BLA_df_final %>% filter(Experiment == 'CX3CL1(2nM)') %>% plot_pie2(AP_amp1_all, "CX3CL1(2nM)") + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_frak5nM_apa <- BLA_df_final %>% filter(Experiment == 'CX3CL1(5nM)') %>% plot_pie2(AP_amp1_all, "CX3CL1(5nM)") + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_antifrak_apa <- BLA_df_final %>% filter(Experiment == 'anti-CX3CR1 + \nCX3CL1(2nM)') %>% plot_pie2(AP_amp1_all, 'anti-CX3CR1 + \nCX3CL1(2nM)') + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_azdfrak_apa <- BLA_df_final %>% filter(Experiment == 'AZD8797 + \nCX3CL1(2nM)') %>% plot_pie2(AP_amp1_all, "AZD8797 + \nCX3CL1(2nM)") + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_azd_apa <- BLA_df_final %>% filter(Experiment == "AZD8797") %>% plot_pie2(AP_amp1_all, "AZD8797") + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_minofrak_apa <- BLA_df_final %>% filter(Experiment == 'minocycline + \nCX3CL1(2nM)') %>% plot_pie2(AP_amp1_all, 'minocycline + \nCX3CL1(2nM)') + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_mino_apa <- BLA_df_final %>% filter(Experiment == 'minocycline') %>% plot_pie2(AP_amp1_all, "minocycline") + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_picro_apa <- BLA_df_final %>% filter(Experiment == 'picrotoxin + \nCGP52432 + \nCX3CL1(2nM)') %>% plot_pie2(AP_amp1_all, 'picrotoxin + \nCGP52432 + \nCX3CL1(2nM)') + theme(plot.title = element_text(size= 10, hjust = 0.5))


# FAST AHP
bp_BLA_fast <- plot_boxplot(BLA_df_final, AHPf1_all, ylabel = "fast AHP (pA)", mtitle = "BLA", vary1 = -25, vary2 = 7, dot_size = 2)
bp_BLA_fast <- bp_BLA_fast + facet_wrap(~ Experiment, nrow = 1, scales = "free_x") + theme(plot.title = element_text(size= 16, face="bold"), axis.text.x = element_text(angle = 30, vjust = 0.7, hjust=0.5)) #+ stat_compare_means(method = 't.test', hide.ns = TRUE, label = 'p.signif', paired = TRUE, label.x.npc = 'center', var.equal = TRUE)

bp_BLA_inter_fast <- plot_boxplot(BLA_df_inter, AHPf1_all, ylabel = "fast AHP (pA)", mtitle = "BLA - interneurons", vary1 = -25, vary2 = -10, dot_size = 2)
bp_BLA_inter_fast <- bp_BLA_inter_fast + facet_wrap(~ Experiment, nrow = 1, scales = "free_x") + theme(plot.title = element_text(size= 16, face="bold"), axis.text.x = element_text(angle = 30, vjust = 0.7, hjust=0.5)) #+ stat_compare_means(method = 't.test', hide.ns = TRUE, label = 'p.signif', paired = TRUE, label.x.npc = 'center', var.equal = TRUE)

pie_BLA_frak_fast <- BLA_df_final %>% filter(Experiment == 'CX3CL1(2nM)') %>% plot_pie2(AHPf1_all, "CX3CL1(2nM)") + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_frak5nM_fast <- BLA_df_final %>% filter(Experiment == 'CX3CL1(5nM)') %>% plot_pie2(AHPf1_all, "CX3CL1(5nM)") + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_antifrak_fast <- BLA_df_final %>% filter(Experiment == 'anti-CX3CR1 + \nCX3CL1(2nM)') %>% plot_pie2(AHPf1_all, 'anti-CX3CR1 + \nCX3CL1(2nM)') + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_azdfrak_fast <- BLA_df_final %>% filter(Experiment == 'AZD8797 + \nCX3CL1(2nM)') %>% plot_pie2(AHPf1_all, "AZD8797 + \nCX3CL1(2nM)") + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_azd_fast <- BLA_df_final %>% filter(Experiment == "AZD8797") %>% plot_pie2(AHPf1_all, "AZD8797") + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_minofrak_fast <- BLA_df_final %>% filter(Experiment == 'minocycline + \nCX3CL1(2nM)') %>% plot_pie2(AHPf1_all, 'minocycline + \nCX3CL1(2nM)') + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_mino_fast <- BLA_df_final %>% filter(Experiment == 'minocycline') %>% plot_pie2(AHPf1_all, "minocycline") + theme(plot.title = element_text(size= 10, hjust = 0.5))
pie_BLA_picro_fast <- BLA_df_final %>% filter(Experiment == 'picrotoxin + \nCGP52432 + \nCX3CL1(2nM)') %>% plot_pie2(AHPf1_all, 'picrotoxin + \nCGP52432 + \nCX3CL1(2nM)') + theme(plot.title = element_text(size= 10, hjust = 0.5))




figure1 <- ggarrange(#ggarrange(bp_BLA_gain, nrow =1), #first row - gain
                     #ggarrange(pie_BLA_frak_gain, pie_BLA_frak5nM_gain, pie_BLA_antifrak_gain, pie_BLA_azdfrak_gain, pie_BLA_azd_gain, pie_BLA_minofrak_gain, pie_BLA_mino_gain, pie_BLA_picro_gain, nrow = 1, common.legend = TRUE, legend = 'bottom'), # pie charts - gain
                    # ggarrange(bp_BLA_inter_gain, NA, nrow =1), # interneurons
                     ggarrange(bp_BLA_thres, nrow =1), #first row - thres
                     ggarrange(pie_BLA_frak_thres, pie_BLA_frak5nM_thres, pie_BLA_antifrak_thres, pie_BLA_azdfrak_thres, pie_BLA_azd_thres, pie_BLA_minofrak_thres, pie_BLA_mino_thres, pie_BLA_picro_thres, nrow = 1, common.legend = TRUE, legend = 'bottom'), # pie charts - thres
                   #  ggarrange(bp_BLA_inter_thres, NA, nrow =1), # interneurons
                   #  ggarrange(bp_BLA_adap, nrow =1), #first row - adap
                   #  ggarrange(pie_BLA_frak_adap, pie_BLA_frak5nM_adap, pie_BLA_antifrak_adap, pie_BLA_azdfrak_adap, pie_BLA_azd_adap, pie_BLA_minofrak_adap, pie_BLA_mino_adap, pie_BLA_picro_adap, nrow = 1, common.legend = TRUE, legend = 'bottom'), # pie charts - adap
                   #  ggarrange(bp_BLA_inter_adap, NA, nrow =1), # interneurons
                   #  ggarrange(bp_BLA_rm, nrow =1), #first row - rm
                   #  ggarrange(pie_BLA_frak_rm, pie_BLA_frak5nM_rm, pie_BLA_antifrak_rm, pie_BLA_azdfrak_rm, pie_BLA_azd_rm, pie_BLA_minofrak_rm, pie_BLA_mino_rm, pie_BLA_picro_rm, nrow = 1, common.legend = TRUE, legend = 'bottom'), # pie charts - rm
                   #  ggarrange(bp_BLA_inter_rm, NA, nrow =1), # interneurons
                   #  ggarrange(bp_BLA_tau, nrow =1), #first row - tau
                   #  ggarrange(pie_BLA_frak_tau, pie_BLA_frak5nM_tau, pie_BLA_antifrak_tau, pie_BLA_azdfrak_tau, pie_BLA_azd_tau, pie_BLA_minofrak_tau, pie_BLA_mino_tau, pie_BLA_picro_tau, nrow = 1, common.legend = TRUE, legend = 'bottom'), # pie charts - tau
                   #  ggarrange(bp_BLA_inter_tau, NA, nrow =1), # interneurons
                  #   ggarrange(bp_BLA_cap, nrow =1), #first row - cap
                  #   ggarrange(pie_BLA_frak_cap, pie_BLA_frak5nM_cap, pie_BLA_antifrak_cap, pie_BLA_azdfrak_cap, pie_BLA_azd_cap, pie_BLA_minofrak_cap, pie_BLA_mino_cap, pie_BLA_picro_cap, nrow = 1, common.legend = TRUE, legend = 'bottom'), # pie charts - cap
                 #    ggarrange(bp_BLA_inter_cap, NA, nrow =1), # interneurons
                  #   ggarrange(bp_BLA_vm, nrow =1), #first row - vm
                  #   ggarrange(pie_BLA_frak_vm, pie_BLA_frak5nM_vm, pie_BLA_antifrak_vm, pie_BLA_azdfrak_vm, pie_BLA_azd_vm, pie_BLA_minofrak_vm, pie_BLA_mino_vm, pie_BLA_picro_vm, nrow = 1, common.legend = TRUE, legend = 'bottom'), # pie charts - vm
                   #  ggarrange(bp_BLA_inter_vm, NA, nrow =1), # interneurons
                   #  ggarrange(bp_BLA_apw, nrow =1), #first row - apw
                   #  ggarrange(pie_BLA_frak_apw, pie_BLA_frak5nM_apw, pie_BLA_antifrak_apw, pie_BLA_azdfrak_apw, pie_BLA_azd_apw, pie_BLA_minofrak_apw, pie_BLA_mino_apw, pie_BLA_picro_apw, nrow = 1, common.legend = TRUE, legend = 'bottom'), # pie charts - apw
                   #  ggarrange(bp_BLA_inter_apw, NA, nrow =1), # interneurons
                   #  ggarrange(bp_BLA_apa, nrow =1), #first row - apa
                   #  ggarrange(pie_BLA_frak_apa, pie_BLA_frak5nM_apa, pie_BLA_antifrak_apa, pie_BLA_azdfrak_apa, pie_BLA_azd_apa, pie_BLA_minofrak_apa, pie_BLA_mino_apa, pie_BLA_picro_apa, nrow = 1, common.legend = TRUE, legend = 'bottom'), # pie charts - apa
                  #   ggarrange(bp_BLA_inter_apa, NA, nrow =1), # interneurons
                  #   ggarrange(bp_BLA_fast, nrow =1), #first row - fast
                   #  ggarrange(pie_BLA_frak_fast, pie_BLA_frak5nM_fast, pie_BLA_antifrak_fast, pie_BLA_azdfrak_fast, pie_BLA_azd_fast, pie_BLA_minofrak_fast, pie_BLA_mino_fast, pie_BLA_picro_fast, nrow = 1, common.legend = TRUE, legend = 'bottom'), # pie charts - fast
                   #  ggarrange(bp_BLA_inter_fast, NA,  nrow =1), # interneurons
                   #  ggarrange(bp_BLA_sag, nrow =1), #first row - sag
                   #  ggarrange(pie_BLA_frak_sag, pie_BLA_frak5nM_sag, pie_BLA_antifrak_sag, pie_BLA_azdfrak_sag, pie_BLA_azd_sag, pie_BLA_minofrak_sag, pie_BLA_mino_sag, pie_BLA_picro_sag, nrow = 1, common.legend = TRUE, legend = 'bottom'), # pie charts - sag
                   #  ggarrange(bp_BLA_inter_sag, NA, nrow =1), # interneurons
                     nrow = 2, heights = c(1, 0.8)) # , 1, 1, 0.8, 1, 1, 0.8, 1, 1, 0.8, 1, 1, 0.8, 1, 1, 0.8, 1, 1, 0.8, 1, 1, 0.8, 1, 1, 0.8, 1, 1, 0.8, 1
figure1



```


## PhD thesis founding
This PhD thesis and candidate were supported by:   

* **National Science Centre Poland doctoral scholarship, ETIUDA**: Wpływ wybranych chemokin na właściwości komórek nerwowych i przekaźnictwo synaptyczne w obszarze kompleksu ciała migdałowatego szczura [Effects of chosen chemokines on neuronal properties and synaptic transmission in central and basolateral complex of the rat amygdala], UMO-2019/32/T/NZ4/00592 - grant holder 2019-2020

* **National Science Centre Poland Grant, PRELUDIUM**: 	Wpływ wybranych chemokin na aktywność oraz transmisję synaptyczną neuronów w centralnym i podstawnobocznym kompleksie ciała migdałowatego [Effects of chosen chemokines on neuronal activity and synaptic transmission in central and basolateral complex of the amygdala], UMO-2016/21/N/NZ4/03621, grant holder 2016-2020 <!--(grant holder: Joanna Ewa Sowa)-->

## PhD candidate’s scientific activity
### Regarding PhD thesis
#### Publications
#### Oral presentations
#### Posters

### Other
#### Publications
#### Oral presentations
#### Posters

